IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-08-01 review/response_2.tex

			For GP Algorithm~\ref{M-al:gp}, the computational complexity is exponential w.r.t. the number of subbands \cite{M-Chiang2005}.
			\begin{framed}
				The joint waveform amplitude and splitting ratio design is summarized in the GP Algorithm~\ref{M-al:gp}, which achieves local optimality at the cost of exponential computational complexity \cite{M-Chiang2005}.
			\end{framed}

			For M-SCA Algorithm~\ref{M-al:m_sca}, each optimization problem involved is an SDP with $(L+1)$ variables and linear constraints, and the computational complexity is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$ where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations.
			\begin{framed}
				Compared with Algorithm~\ref{M-al:sca}, the rate constraint \eqref{M-co:irs_rate} is dropped and each SDP in Algorithm~\ref{M-al:m_sca} involves $(L+1)$ linear constraints. Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{M-al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{M-Luo2010}. Note that $I_{\mathrm{M-SCA}}=1$ for the WIT point since the current expression is dropped and no SCA is involved.
			\end{framed}

			For BCD Algorithm~\ref{M-al:bcd}, since Algorithm~\ref{M-al:gp} is involved per iteration, the computational complexity is exponential w.r.t. the number of subbands.
			\begin{framed}
				The steps are summarized in the BCD Algorithm~\ref{M-al:bcd}, whose computational complexity is exponential as inherited from Algorithm~\ref{M-al:gp}.
			\end{framed}

@@

		\begin{response}
			Thank you for sharing this paper. Instead of optimizing the phase shift of each IRS element, it tailored a tile-based two-stage optimization framework for large-scale IRS to enable a flexible performance-complexity tradeoff. The model also adapts well to practical IRS models accounting AoA and AoD. In contrast, our paper is more focused on waveform design and rate-energy tradeoff for one SWIPT user with practical co-located information decoder and energy harvester. We have updated the manuscript as follows.
			\begin{framed}
				In \cite{Xu2021}, the authors proposed a scalable resource allocation framework for SWIPT systems involving large-scale IRS, where the reflectors are grouped into tiles and the optimization process is divided into an offline mode-design stage and an online mode-selection stage to reduce overall complexity. It was concluded that the tile-based two-stage algorithm not only enables a flexible balance between performance and complexity but also adapts well to the physics-based IRS model accounting AoA and AoD. To the best of our knowledge, all existing IRS-aided SWIPT papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network. In this paper, we instead build our design based on a proper nonlinear harvester modeling that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with practical co-located information decoder and energy harvester.
			\end{framed}
		\end{response}

		\begin{point}
			It could be better if the authors can provide some references for the parameter values chosen in the simulation part.
		\end{point}

		\begin{response}
			The system layout follows \cite{M-Wu2019} and we set the AP-UE distance to be larger than SWIPT literatures \cite{M-Clerckx2018b} and experiments \cite{M-Kim2020a} thanks to the IRS. For the center frequency, we consider \SI{2.4}{\GHz} due to its ubiquitous and license-free properties. Note that the path loss can be greatly reduced (and the R-E performance can be improved) if the system operates at much lower frequency, as considered in most IRS papers. In the previous manuscript, we made a mistake in the choice of reference path loss. As indicated by Comment~\ref{pt:3.3}, even the free-space path loss should be around \SI{40}{\dB} at \SI{1}{\meter}. To fix this issue, we updated the path loss model as IEEE TGn channel model D that is representative of small environments such as residential homes and small offices \cite{M-Erceg2004}. It has three clusters with \SI{50}{\ns} r.m.s. delay spread, and the path loss exponent is set to \num{2} (i.e., free-space model) up to breakpoint distance \SI{10}{\meter} and set to \num{3.5} onwards. This has a similar effect to most IRS literatures that assign a relatively large path loss exponent to the direct path and smaller ones to the incident and reflected paths to penalize the channel with large distance. As for the rectenna parameters, we forgot to mention that the parameters are taken from \cite{M-Clerckx2016a} and have added the reference to the revised manuscript.
		\end{response}

@@

	\begin{reviewer}
		\begin{point}
			Although this paper reveals many useful insights, most of them are obtained via simulation and then explained via text. The overall theoretical contributions can be greatly improved if the authors can analytically verify or prove some of them, especially those unique to this paper. The authors may conduct the analysis under some simplified or special cases. If some of the observations and findings have been verified in existing papers, the authors can cite and echo these papers wherever necessary.
		\end{point}

		\begin{response}
			We believe the reviewer was referring to the array gain and scaling law suggested by Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}. Recall that $M$ refers to the number of transmit antenna, $N$ refers to the number of subbands, and $L$ refers to the number of IRS elements. From the perspective of WIT, coherent transmission achieves an array gain of $M$ \cite{M-Tse2005} and coherent reflection achieves an array gain of $L^2$ \cite{M-Wu2019}. From the perspective of WPT, \cite{M-Clerckx2016a} and \cite{M-Clerckx2018b} analytically proved the scaling law of the multisine waveform. Even if a suboptimal waveform scheme (uniform power allocation in the frequency domain and matched filter in the spatial domain) is used, when $M$ is sufficiently large, the expectation of the DC current scales quadratically with $M$. We have cited those papers in the revised manuscript.

			Next, we verify the last observation where the expectation of the DC current scales quartically with $L$ in a much simplified scenario. Consider a SISO WPT system in a frequency-flat channel. We assume a sufficiently large $L$ such that the auxiliary link is dominant and the contribution of direct channel is omitted. With uniform power allocation ($s_n = \sqrt{2P}/\sqrt{N}$) in the frequency domain, the DC current writes as
			\begin{equation}
				z_{\mathrm{UP}} = \beta_2 (\Lambda_{\mathrm{I}} \Lambda_{\mathrm{R}} L \lvert X \rvert)^2 P + \frac{3}{8} \beta_4 (\Lambda_{\mathrm{I}} \Lambda_{\mathrm{R}} L \lvert X \rvert)^4 F,
			\end{equation}
			where $\beta_2$ and $\beta_4$ are fixed rectenna parameters, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{R}}$ are the path loss of incident and reflected links, $X$ is the random variable that models the small-scale double fading through one IRS element at any subband, and
			\begin{equation}
				F = \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} s_{n_1} s_{n_2} s_{n_3} s_{n_4} = \frac{4(2N^2+1)}{3N}.
			\end{equation}
			Taking expectation over $\lvert X \rvert$, we have
			\begin{equation}
				\bar{z}_{\mathrm{UP}} = \beta_2 \Lambda_{\mathrm{I}}^2 \Lambda_{\mathrm{R}}^2 L^2 \mathbb{E}\{\lvert X \rvert^2\} P + \frac{3}{8} \beta_4 \Lambda_{\mathrm{I}}^4 \Lambda_{\mathrm{R}}^4 L^4 \mathbb{E}\{\lvert X \rvert^4\} \frac{2N^2+1}{2N} P^2,
			\end{equation}
			which verifies the scaling order of $L^4$. The analysis is not presented in the manuscript due to the space constraint.
		\end{response}

@@

				\textellipsis the LC-BCD algorithm draws the R-E tradeoff by performing a two-dimensional search that adjusts the combining and splitting ratios from \num{1} to \num{0}.

				\textellipsis assume $\delta=\rho$ for simplicity (hence one-dimensional search to obtain the R-E region).

				\textellipsis \emph{Third,} the LC-BCD algorithm achieves a very good R-E performance even if one-dimensional search is considered for $\delta=\rho$ over $[0,1]$. This conclusion is also verified in the following plots.
			\end{framed}
			\footnotetext{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point. Heuristically, $\delta^{\star}$ and $\rho^{\star}$ should approximately equal at each point to boost R-E tradeoff.}
		\end{response}

		\begin{point}
			If possible, in Figs.~\ref{M-fi:re_irs_1mhz} and \ref{M-fi:re_irs_10mhz}, the authors can show the performance of the design under the conventional linear harvester model, so as to show how much performance loss it would incur.
		\end{point}

		\begin{response}
			We would like to clarify that the performance loss under the conventional linear harvester model is revealed instead in Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}. Figs.~\ref{M-fi:re_irs_1mhz} and \ref{M-fi:re_irs_10mhz} are intended to compare different IRS strategies when both waveform and passive beamforming are designed under nonlinear harvester model. The authors believe that to design passive beamforming under linear harvester model when the waveform is designed under nonlinear harvester model might confuse the readers. On the other hand, we agree with the reviewer that the performance loss under linear harvester deserves more attention, and have changed the label in Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector} from `ASS' to `LEH' and revised the manuscript as follows to make this point clear.
			\begin{framed}
				\emph{Second,} the conventional Linear Energy Harvester (LEH) model leads to power-inefficient design. To show the underlying performance loss, we truncate the DC objective function \eqref{M-eq:z} at $n_0=2$ such that, 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required, 2) in the waveform design problem, the WPT-optimal strategy is the Adaptive Single Sinewave (ASS) waveform strategy that allocates all power to the multisine at the strongest subband \cite{M-Clerckx2016a}. As shown in Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dB} current gap compared to SMF and GP.
			\end{framed}
		\end{response}

@@

		\begin{response}
			We sincerely appreciate the reviewer for pointing out this issue. Indeed, the local optimality is not guaranteed as \eqref{M-co:original_rate} couples all blocks together. We have removed the claim on optimality and updated Proposition~\ref{M-pr:bcd} as follows.
			\begin{framed}
				For any feasible initial point, the BCD Algorithm~\ref{M-al:bcd} is guaranteed to converge.
			\end{framed}
			The proof has been modified correspondingly.
			\begin{framed}
				The objective function \eqref{M-ob:original} is non-decreasing over the iterations, because the IRS phase shift by Algorithm~\ref{M-al:sca} is local optimal, the active precoder by \eqref{M-eq:b_n} is global optimal, and the waveform amplitude and splitting ratio by Algorithm~\ref{M-al:gp} are local optimal. \eqref{M-ob:original} is also upper-bounded due to the unit-modulus constraint \eqref{M-co:original_modulus} and the transmit power constraint \eqref{M-co:original_power}. Therefore, Algorithm~\ref{M-al:bcd} is guaranteed to converge. However, it may not converge to optimal points since variables are coupled in constraint~\eqref{M-co:original_rate} \cite{M-Grippo2000}.
			\end{framed}
		\end{response}

		\begin{point}
			The figures are too small. For example, Fig.~\ref{M-fi:scaling_reflector}, the axis legend is not fully shown.
		\end{point}

		\begin{response}
			We apologize for the inconvenience. The figures have been amplified and the legends have been calibrated.
		\end{response}

		\begin{point}
			It is said that the reference path loss is \SI{35}{\dB} at \SI{1}{\meter}, while for the center frequency at \SI{5.18}{\GHz}, even adopting the free space path loss model also will lead a much sever path loss at \SI{1}{\meter}. It is not clear how the authors calculate this.
			\label{pt:3.3}
		\end{point}

		\begin{response}
			We agree with the reviewer that the reference path loss used in the simulation is faulty and we sincerely apologize for this issue. The parameter \SI{35}{\dB} was considered in some IRS literatures without specifying the operating frequency, and it was taken in the previous simulations without a second consideration. In the corrected manuscript, we instead consider a center frequency at \SI{2.4}{\GHz} that corresponds to a free-space path loss of \SI{40}{\dB} at \SI{1}{\meter}. The path loss used in the simulation is taken from IEEE TGn channel model D \cite{M-Erceg2004} where the slope is set to \num{2} (i.e., free-space model) up to breakpoint distance \SI{10}{\meter} and \num{3.5} onwards. This has a similar effect to most IRS literatures that assign a relatively large path loss exponent to the direct path and smaller ones to the incident and reflected paths to penalize the channel with large distance.

			To avoid rerunning the simulation, in the updated manuscript, we raise the EIRP from \SI{36}{\dBm} to \SI{40}{\dBm} (which still complies with FCC regulations \cite{Afar2021}) and change the receive antenna gain from \SI{2}{\dBi} to \SI{3}{\dBi} to compensate the \SI{5}{\dB} difference. Please refer to the following specification for details.
			\begin{framed}
				We consider a large open space Wi-Fi-like environment at \SI{2.4}{\GHz} center frequency where the channel is modeled by IEEE TGn channel model D \cite{M-Erceg2004}. Specifically, the path loss exponent is set to \num{2} (i.e., free-space model) up to a breakpoint distance of \SI{10}{\meter}, and set to \num{3.5} onwards. All fadings are modeled as Non-Line-of-Sight (NLoS) with tap delays and powers specified by model D. The tap gains are modeled as i.i.d. CSCG variables. Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$ \cite{M-Clerckx2016a}. We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (hence one-dimensional search to obtain the R-E region).
			\end{framed}
		\end{response}

### 2021-08-01 assets/waveform_wpt_modulated.tex
:bento: Update assets

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,3.312in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	4.47213595499958\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{I}}$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	4.47213595499958\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{No IRS: {\boldmath${s}$}$_{\mathrm{I}}$}

@@

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,2.598in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	3.16127375477314\\
2	3.16328124696217\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	3.16000164000459\\
2	3.16455204336543\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,1.883in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=4.47213595499958,
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	2.23287518822941\\
2	2.2349269985345\\
3	2.23712082213722\\
4	2.2393436833526\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	2.23243942623434\\
2	2.23535811809091\\
3	2.23559687073864\\
4	2.24086923394096\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,1.168in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.56947570711734\\
2	1.57851757716824\\
3	1.58044033841813\\
4	1.58155392693919\\
5	1.58198101788601\\
6	1.58501068613205\\
7	1.5854415059255\\
8	1.58662414938375\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.56539227519679\\
2	1.57784161002588\\
3	1.57927371173129\\
4	1.58176667731984\\
5	1.58367655185228\\
6	1.58456745246925\\
7	1.58798555735369\\
8	1.58848608357287\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,0.454in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.10024627987476\\
2	1.10664679147412\\
3	1.11204358490005\\
4	1.11548794498246\\
5	1.11636022580843\\
6	1.11667878555116\\
7	1.11706894724375\\
8	1.11773783143934\\
9	1.11958645829829\\
10	1.12088764958973\\
11	1.1221919201651\\
12	1.12315337822569\\
13	1.12435794296855\\
14	1.12469670812645\\
15	1.12549793104218\\
16	1.12556826383419\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.09504669861652\\
2	1.10317579191466\\
3	1.11227601228037\\
4	1.11361418816502\\
5	1.11483774301138\\
6	1.11656722620907\\
7	1.11743910790233\\
8	1.11769734992669\\
9	1.11854798737502\\
10	1.12003038718696\\
11	1.12377646668063\\
12	1.12467567262626\\
13	1.12655148101693\\
14	1.1274126433068\\
15	1.12796634097065\\
16	1.12836437582839\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

>>>>

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,3.312in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	4.47213594256269\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{I}}$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	4.47213594337198\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{No IRS: {\boldmath${s}$}$_{\mathrm{I}}$}

@@

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,2.598in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.0184995683160857\\
2	4.47209768702344\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.129245877350812\\
2	4.47026793562064\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,1.883in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=4.47213595499958,
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.22062490140461e-05\\
2	1.39192509615866e-05\\
3	0.000167256169027754\\
4	4.30544303806377\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	9.33422606187999e-05\\
2	0.00147978695861402\\
3	0.00191364123320196\\
4	4.17157348848167\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,1.168in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.79407563422514e-05\\
2	1.85714620268948e-05\\
3	1.93369863129044e-05\\
4	2.05312064086965e-05\\
5	2.39372760743564e-05\\
6	0.000270300028092872\\
7	0.0016215086351542\\
8	0.0160756710767743\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	2.10931097834311e-05\\
2	0.000139552824561586\\
3	0.000276023439508691\\
4	0.00106782286234867\\
5	0.00351285453513694\\
6	0.00648184617722918\\
7	0.107736181700373\\
8	0.176305935466697\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,0.454in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	2.1710720676869e-05\\
2	2.17376236559091e-05\\
3	2.17546727036312e-05\\
4	2.17704747375875e-05\\
5	2.1794882595919e-05\\
6	2.18143527307804e-05\\
7	2.18457881093868e-05\\
8	2.19305951527728e-05\\
9	2.19328455198334e-05\\
10	2.21325751565748e-05\\
11	2.22071274039942e-05\\
12	2.25919792561307e-05\\
13	2.32407144765052e-05\\
14	3.96822628633167e-05\\
15	7.14362303625945e-05\\
16	0.000113723656309437\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	2.55678240861943e-05\\
2	2.83329978735535e-05\\
3	0.000111062823999827\\
4	0.000152254112563635\\
5	0.000208409153895756\\
6	0.000340769670268019\\
7	0.000442331617111308\\
8	0.000478575211543757\\
9	0.000624300142407434\\
10	0.00101777812439063\\
11	0.00411301301403382\\
12	0.00600022404275364\\
13	0.0141022990885949\\
14	0.0215927071517045\\
15	0.0287996793460057\\
16	0.035646104685323\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%
